\documentclass[10pt,a4paper]{report}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{latexsym}

\begin{document}
\paragraph{First Turn} Decide what the initial stauts is.

\paragraph{Your Turn}
Draw two cards and describe what happens.

\paragraph{Suit meaning}
Each suit has a meaning to drive your descriptions.
\begin{description}
\item[$\diamondsuit$] Calm, Stagnancy, Wait, Resistence, Aid, Friensdhip, \textbf{Summer}
\item[$\spadesuit$] Depletion, Decay, Extinction, Doom, End, Inhibition, \textbf{Winter}
\item[$\heartsuit$] Growth, Prosperity, Resourcefulness, Begin, Blossom, Birth, \textbf{Spring}
\item[$\clubsuit$] Unexpected, Treason, Trial, Action, Solution-Force, Aggressivity, \textbf{Autumn}
\end{description}

\paragraph{Rank meaning}
Each rank has a power to drive your descriptions.

\begin{description}
\item 1 Animal Tribe.
\item 2 Beast Tribe.
\item 3 Humanoids (small).
\item 4 Humanoids (large).
\item 5 Magical Beasts (small).
\item 6 Magical Beasts (large).
\item 7 Aberrations.
\item 8 \"{U}ber-Creatures.
\item 9 Unique-Creature.
\item Vallet Warrior, Hero, Leader, Soldier, Brute.
\item Queen Saint, Holy, Blaspheme, Abyssal, Envoy.
\item King Great-Ruler, God-like.
\item Joker Choose whatever you like.
\end{description}

\paragraph{Fight}
Clashes can take place. They are resolved as follows.
\begin{itemize}
\item Draw one card.
\item Add to indiviudal power half the value of the card rounded down.
\item Figure always wins against non-figures.
\item Compare combined individual power.
\item The higher value wins.
\item Defenders win ties.
\end{itemize}

\paragraph{Rules}
There are some simple rules you may want to know.
\begin{itemize}
\item You can add/subtract cards power one another.
\item No figure can be obtained/tamed in this manner.
\item Extreme calls can be made by drawing +1 cards, but all must be accepted. Mind the consequences.
\end{itemize}

\begin{tabular}{l|c}
\hline
\textbf{Facet} & \textbf{Meaning}\\
\hline
Goose	&	Seduction (Charisma)/Shallowness (Voluptivity, Illusion, Lust)\\
Autumn	 & 	Plenty (Satisfaction, Wellness)/Want (Quest)\\
Spring	&	Rebirth (Change)/Effimerity (Childhood, Inexperience)\\
Jackal	&	Fight (Clash, Strife)/Pillage (Brutality)\\
Boar	&	Family (Protection)/Blind fury (Fanatism, Shortsighted)\\
Law		 &	Justice/Punishment\\
Queen	&	Splendor (Beauty)/Pride (Hybriss)\\
Coin	&	Bargain (Pact, Exchange)/Bribe (Compromise)\\
Dice	&	Luck (Favor, Fate)/Chaos\\
King	&	Order (Duty, Loyalty)/Tiranny (Cohercition, Control, Compulsion)\\
Hermit	&	Divine (Contemplation)/Isolation\\
Winter	&	Envy/Rest (Peace, Pause)\\
Death	&	Loss/Accomplishment (End)\\
Priestess &	Virtue/Waste (Inactivity, Sloth)\\
Star	&	Guidance (Opportunity)/Distance (Difficulty, Fatigue, Exahustion, Ban)\\
Key	    &	Secret (Darkness)/Truth revealed\\
Unicorn	&	Purity (Miracle, Mend)/Sacrifice\\
Old Man	&	Memory/Decay (Wound, Sorrow, Weakness)\\
Chimera	&	Danger  (Mutation, Abomination)/Dream (Ideal)\\
Basilisk &	Life (Strength)/Poison (Treachery)\\
\hline
\end{tabular}
\end{document}